---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# uspop

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/skaltman/uspop/branch/master/graph/badge.svg)](https://codecov.io/gh/skaltman/uspop?branch=master)
<!-- badges: end -->

uspop makes it easy to retrieve historical U.S. population estimates for states, counties, or the entire country. 

All estimates are from the Census Bureau's [Vintage 2019 Population Estimates API](https://www.census.gov/data/developers/data-sets/popest-popproj/popest.Vintage_2019.html). 

## Installation

You can install uspop from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("skaltman/uspop")
```
## Retrieve populations

```{r}
library(uspop)
```


You can retrieve population estimates from 2010-2019 for the entire U.S., states, or counties.

```{r example, message = FALSE, eval=FALSE}
# Entire U.S.
population(geography = "us")

# All states
population(geography = "state")

# All counties
population(geography = "county")
```

Each resulting tibble has four columns:

* `region`
* `fips`
* `year`
* `pop`

```{r message=FALSE}
population(geography = "us")
```

`fips` is `"0"` for the United States, and the state or county FIPS for states and counties.

