---
title: "Working with U.S. population data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{population-data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
library(uspop)
```

## Population Estimates API

The Census Bureau publishes a wide variety of APIs, including many that supply population data. Both the decennial census and American Community Survey (ACS) include population data, but the Population Estimates APIs:

* Are more accurate than the ACS estimates.
* Provide yearly data, as opposed to data every ten years like the decennial census. 

`uspop::population()` uses the Vintage 2019 Population Estimates API to pull accurate population estimates for 2010-2019.

## Geographies

`uspop::population()` currently only supports three geographies: 

* `"us"`: The population of the entire U.S.
* `"state"`: Population by state, for all states.
* `"county"`: Population by county, for all counties. 

`population()` currenlty does not support limiting the data to a particular set of states or counties. However, you can filter after calling `population()`. For example, if you only want data for the state of Montana:

```{r}
population("state") %>% 
  filter(region == "Montana")
```

Or, if you want the counties from Montana:
```{r}
# 30 is Montana's state FIPS
population("county") %>% 
  filter(str_detect(fips, "^30"))
```

## Working directly with the APIs

If you'd like to work directly with the Census Bureau's APIs, [this chapter](https://dcl-wrangle.stanford.edu/census.html) has more information.
